Alternative Methods for Implementing Explicit and Finding Implicit Sharing in embedded DSLs

### 2022-12-13 paper/paper.tex
working on issues with hash-consing in prototype and paper

We can then create different instances to implement different functionality.
For example, we can generate the AST from the previous DSL like so
\begin{minted}{haskell}
data ExpR a = ExpR { unExpR :: Exp }

@@

And use the same DSL code to run either implementation
\begin{minted}{haskell}
exp :: repr Int -> repr Int
exp v0 =
  let
    exp0 = add v0 (constant 0)
  in add exp0 exp0

@@

data BiMap a -- abstract
lookup_key : Ord a => a -> BiMap a -> Maybe Int
lookup_val : Int -> BiMap a -> a
insert : Ord a => a -> BiMap a -> (Int,BiMap a)
empty : BiMap a

>>>>

We can then create different instances to implement different functionality.
For example, we can generate the AST from the previous DSL like so
\begin{minted}{haskell}
newtype ExpR a = ExpR { unExpR :: Exp }

@@

And use the same DSL code to run either implementation
\begin{minted}{haskell}
exp :: Exp repr => repr Int -> repr Int
exp v0 =
  let
    exp0 = add v0 (constant 0)
  in add exp0 exp0

@@

data BiMap a -- abstract
lookup_key :: Ord a => a -> BiMap a -> Maybe Int
lookup_val :: Int -> BiMap a -> a
insert :: Ord a => a -> BiMap a -> (Int,BiMap a)
empty :: BiMap a
